Supplementary Information

### 2015-06-22 manuscript/latitudepaper.tex
updated figures and compiled
took care of the easy fixes

\section*{Figures}
\begin{figure}[h]
\includegraphics[width=.85\textwidth]{Figures/by_TL/scaling_with_S/proportions/fitlines_nonts.eps}
\caption{Scaling relationships for re-scaled link density, generality, and vulnerability 
relative to species richness and the proportions of basal resources (\% Basal), intermediate 
consumers (\% Intermediate), or top predators (\% Top) in a food web. Link density, generality,
and vulnerability were re-scaled to remove the effects of latitude and, where applicable, ecosystem
type by dividing the observed value of link density, generality, or vulnerability by species richness
or the proportion of species at a given trophic level raised to an exponent including the effects of
latitude, ecosystem type, and their interaction. Note that estuarine food webs were used as the intercept
ecosystem type in all models, but that at most two ecosystem types had interactions between ecosystem type and
latitude retained in the best-fit model (see \emph{results} for specifics). For each relationship, 
we show these rescaled values (white circles), as well as the overall scaling relationship using estuarine
ecosystems as a baseline (N=163 food webs). For a figure with the uncorrected values,
see Fig.~\emph{S1}, \emph{Appendix S4}.}
\label{props_v_lat}
\end{figure}

\begin{figure}[h]
\centerline{\includegraphics*[height=.65\textheight]{Figures/by_TL/marginal/justS_marginal_latitude.eps}}
\caption{Changes to the scaling of link density with species richness across ecosystem
types and over latitude. We show the estimated scaling exponent for species richness (black
line) with its 95\% confidence interval (in grey), based on N=163 empirical food webs.
Latitude is given in degrees from the equator regardless of direction. The
behaviour of exponents for the scaling of generality and vulnerability with
species richness was very  similar to those for link density, except for the
scaling of generality in streams where  the size of the exponent increased
towards the poles. See \emph{Fig. S2, Appendix 5} for  all scaling
relationships.} \label{S} \end{figure}

\begin{figure}[!H]
\centerline{\includegraphics*[height=.65\textheight]{Figures/by_TL/marginal/BIT_marginal_latitude.eps}}
\caption{Changes to the scaling of link density with the proportions of basal resources, intermediate
consumers, or top predators in a food web across ecosystem types and over latitude. For each proportion
we show the estimated scaling exponent (black line) with its 95\% confidence interval (in grey), based
on N=163 empirical food webs. Latitude is given in degrees from the equator regardless of direction. 
The behaviour of exponents for the scaling relationships of generality and vulnerability with each 
proportion was very similar to those of the scaling relationships with link density, except for the 
scaling of generalitywith the proportion of top predators where there was no effect of latitude on the 
size of the exponent in any ecosystem type. See \emph{Figs. S3-S5, Appendix 5} for all scaling relationships.}
\label{BIT}
\end{figure}

>>>>

\section*{Figures}
\begin{figure}[h]
\centerline{\includegraphics*[width=.85\textwidth]{Figures/by_TL/scaling_with_S/proportions/fitlines_nonts.eps}}
\caption{Scaling relationships for re-scaled link density, generality, and vulnerability 
relative to species richness and the proportions of basal resources (\% Basal), intermediate 
consumers (\% Intermediate), or top predators (\% Top) in a food web. Link density, generality,
and vulnerability were each re-scaled to remove the effects of latitude and ecosystem
type. As the these relationships take the form of power laws, we did this by dividing the food-web
property (e.g. link density) by the predictor (e.g. \% Basal) raised to an exponent including the 
effects of latitude and, where applicable, ecosystem type and the interaction between ecosystem
type and latitude. Note that in all cases estuarine food webs were used as the baseline 
ecosystem type, but that at most two ecosystem types had interactions between ecosystem type and
latitude retained in the best-fit model (see \emph{results} for specifics). For each relationship, 
we show the rescaled values (white circles) as well as the overall scaling relationship using estuarine
ecosystems as a baseline (black line, N=163 food webs). For a figure with the uncorrected values,
see Fig.~\emph{S1}, \emph{Appendix S4}.}
\label{props_v_lat}
\end{figure}

\begin{figure}[h]
\centerline{\includegraphics*[height=.65\textheight]{Figures/by_TL/marginal/justS_marginal_latitude.eps}}
\caption{Changes to the scaling of link density with species richness across ecosystem
types and over latitude. We show the estimated scaling exponent for species richness (black
line) with its 95\% confidence interval (in grey), based on N=163 empirical food webs.
Latitude is given in degrees from the equator regardless of direction. The
behaviour of exponents for the scaling of generality and vulnerability with
species richness was very  similar to those for link density, except for the
scaling of generality in streams where  the size of the exponent increased
towards the poles. See Fig.~\emph{S2, Appendix 5} for  all scaling
relationships.} \label{S} \end{figure}

\begin{figure}[!H]
\centerline{\includegraphics*[height=.65\textheight]{Figures/by_TL/marginal/BIT_marginal_latitude.eps}}
\caption{Changes to the scaling of link density with the proportions of basal resources, intermediate
consumers, or top predators in a food web across ecosystem types and over latitude. For each proportion
we show the estimated scaling exponent (black line) with its 95\% confidence interval (in grey), based
on N=163 empirical food webs. Latitude is given in degrees from the equator regardless of direction. 
The behaviour of exponents for the scaling relationships of generality and vulnerability with each 
proportion was very similar to those of the scaling relationships with link density, except for the 
scaling of generality with the proportion of top predators where there was no effect of latitude on the 
size of the exponent in any ecosystem type. See Figs.~\emph{S3-S5, Appendix 5} for all scaling relationships.}
\label{BIT}
\end{figure}

### 2015-06-22 manuscript/supplement.tex
took care of the easy fixes

  We combined published food webs from~\citet{GlobaWeb} (GlobalWeb),~\citet{Brose2006} (Brose), 
  and~\citet{Dunne2013} (Dunne).
  Of the 385 food webs available from~\citet{Globalweb}, 122 were rejected because their original
  source was unpublished or could not be retrieved. We further eliminated 13 source or sink webs
  (which describe feeding links flowing from or to a particular resource or top predator rather
  than the interactions of an entire community), 8 plant-pollinator webs, 34 host-parasitoid webs,
  and 2 networks describing competitive interactions. Finally, we eliminated 2 webs describing 
  inferred interactions in an extinct community, 8 ``generalized schemes'' that were not based
  on direct field data, and 2 webs where it was not clear which of several described study sites
  were used to construct the food web (and therefore the latitude of the food web could not be 
  included). This left us with 156 webs from~\citet{GlobalWeb}.

  To these, we added 7 webs from~\citet{Dunne2013} that were originally used to assess the roles
  of parasites within food webs. As all but 3 of the webs from~\citet{GlobalWeb} contained only
  free-living species, we removed the the parasites (and all interactions involving them) from
  these webs (and the 3 webs containing parasites from~\citet{GlobalWeb}) leaving free-living 
  species only. In addition, we included the 96 webs from~\citet{Brose2006}, which were originally
  collected to XXXYYYY. This gave us a database of 259 webs. However, as we wished to use the
  logarithmic form of power-law relationships, we then eliminated any food web which did not have
  at least one each of basal resources, intermediate consumers, and top predators (to obtain non-zero
  proportions of each category). Our final sample size was thereby reduced to 163 food webs.

 (See Table S1 for a list of rejected webs and reasons for their
  exclusion.)

@@

    Although scaling relationships between species richness and generality or
    species richness and vulnerability have not been explicitly examined (but see scaling 
    relationships for the standard devaitions of each property in~\citet{Riede2010}), we expect that they will follow
    power laws similar to that of the relationship between species richness and links per species.
    This is because the links taken into account in calculating generality and vulnerability are subsets 
    of the total links included when calculating links per species. As with links per species, we explicitly 
    compared the error distributions of models for generality and vulnerability using
    both the power-law and logarithmic formulations. 
    In each case, we used the best-fitting equation as a template when assessing the effect of latitude on scaling with
    species richness.

@@

    When considering the relationships between species richness or the proportions 
    of basal resources, intermediate consumers, or top predators and all response variables 
    (link density, generality, vulnerability), equation~(\ref{Loglog}) had a
    lower AIC than did equation~(\ref{Power}). This indicates that the
    data support an assumption of multiplicative lognormal error better than an
    assumption of additive normal error. That is, models where $\epsilon$ is
    modelled as an additive term on
    the logarithmic scale provide a better description of the data than models
    where $\epsilon$ is modelled as an additive term on the arithmetic scale.  
    We therefore used logarithmic-form models when assessing the
    effect of latitude on scaling relationships  with species richness.

@@

  \subsubsection*{Results}
    Contrary to the expected latitudinal gradient, the best-fit version of
    equation~(\ref{Latfull}) for species richness did not include a signficant effect of latitude for any ecosystem type except streams
    ($\beta_{Latitude}$=0.095, $p$=0.626; $\beta_{Latitude:Stream}$=-1.69, $p$=0.007).  This
    relationship was robust to the removal of three outliers (based on Cook's Distance). 
    There were also relationships between latitude and link density and latitude and vulnerability
    in stream food webs, but these trends were non-signficant after the removal of three outliers.
    Link density and vulnerability did not vary with latitude in any other ecosystem type.
    The best-fit version of equation~(\ref{Latfull}) for generality did not include any effect of
    latitude in any ecosystem type.

@@

\begin{figure}[h]
\centerline{\includegraphics*[width=.75\textwidth]{Figures/by_TL/scaling_with_S/proportions/fitlines_nonts_observed.eps}}
\caption{Scaling relationships for link density, generality (number of prey), 
and vulnerability (number of predators) against the proportions of basal resources (\% Basal),
intermediate consumers (\% Intermediate), top predators (\% Top), and species richness of a food web. 
For each relationship, we show observed values (grey circles) and the scaling relationship, neglecting 
any effects of habitat type or latitude (N=163 food webs). See Fig. 1 (\emph{Main Text}) to compare with 
observed values correcting for the effects of habitat type and latitude. }
\label{props_v_lat_obs}
\end{figure}

@@

\begin{figure}[h]
\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_proportions.eps}}
\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
types and over latitude. For each property we show the scaling exponent for species richness (black
line) with a 95\% confidence interval (in grey). Latitude is given in degrees from the equator
regardless of direction. The scaling relationships are based on N=163 empirical food webs.}
\label{S}
\end{figure}

\begin{figure}[!h]
\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/B_marginal_latitude_proportions.eps}}
\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
types and over latitude. For each property we show the scaling exponent for the proportion of
basal resources (black line) with a 95\% confidence interval (in grey). Latitude is given in degrees
from the equator regardless of direction. The scaling relationships are based on N=163 empirical food webs.}
\label{B}
\end{figure}

@@

\begin{figure}[h]
\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/I_marginal_latitude_proportions.eps}}
\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
types and over latitude. For each property we show the scaling exponent for the proportion of
intermediate consumers (black line) with a 95\% confidence interval (in grey). Latitude is given in degrees
from the equator regardless of direction. The scaling relationships are based on N=163 empiricl food webs.}
\label{I}
\end{figure}

\begin{figure}[!h]
\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/T_marginal_latitude_proportions.eps}}
\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
types and over latitude. For each property we show the scaling exponent for the proportion of
top predators (black line) with a 95\% confidence interval (in grey). Latitude is given in degrees
from the equator regardless of direction. The scaling relationships are based on N=163 empiricl food webs.}
\label{T}
\end{figure}

>>>>

  We combined published food webs from~\citet{GlobaWeb},~\citet{Brose2006}, 
  and~\citet{Dunne2013}.
  Of the 385 food webs available from~\citet{Globalweb}, 122 were rejected because their original
  source was unpublished or could not be retrieved. We further eliminated 13 source or sink webs
  (which describe feeding links flowing from or to a particular resource or top predator rather
  than the interactions of an entire community), 8 plant-pollinator webs, 34 host-parasitoid webs,
  and 2 networks describing competitive interactions. Finally, we eliminated 2 webs describing 
  inferred interactions in an extinct community, 8 ``generalized schemes'' that were not based
  on direct field data, and 2 webs where it was not clear which of several described study sites
  were used to construct the food web (and therefore the latitude of the food web could not be 
  included). This left us with 156 webs from~\citet{GlobalWeb}.

  To these, we added 7 webs from~\citet{Dunne2013} that were originally used to assess the roles
  of parasites within food webs. As all but 3 of the webs from~\citet{GlobalWeb} contained only
  free-living species, we removed the the parasites (and all interactions involving them) from
  these webs (and the 3 webs containing parasites from~\citet{GlobalWeb}) leaving free-living 
  species only. In addition, we included the 96 webs from~\citet{Brose2006}, which were originally
  collected to XXXYYYY. This gave us a database of 259 webs. As we wished to use the
  logarithmic form of power-law relationships, we then eliminated any food web which did not have
  at least one each of basal resources, intermediate consumers, and top predators (to obtain non-zero
  proportions of each category). Our final sample size was thereby reduced to 163 food webs.

 See Table S1 for a list of rejected webs and reasons for their
  exclusion.

@@

    Although scaling relationships between species richness and generality or
    species richness and vulnerability have not been explicitly examined (but see scaling 
    relationships for the standard devaitions of each property in~\citet{Riede2010}), we expect that they will follow
    power laws similar to that of the relationship between species richness and links per species.
    This is because the links taken into account in calculating generality and vulnerability are subsets 
    of the total links included when calculating links per species. As with links per species, we explicitly 
    compared the error distributions of models for generality and vulnerability using
    both the power-law and logarithmic formulations. 
    In each case, we used the best-fitting equation as a template when assessing the effect of latitude on scaling with
    species richness. We then repeated this analysis 
    to model the scaling of link density, generality, 
    and vulnerability with the proportions of basal 
    resources, intermediate consumers, and top predators
    in a food web.

@@

    When considering the relationships between species richness or the proportions 
    of basal resources, intermediate consumers, or top predators, and all response variables 
    (link density, generality, vulnerability), equation~(\ref{Loglog}) had a
    lower AIC than did equation~(\ref{Power}). This indicates that the
    data support an assumption of multiplicative lognormal error better than an
    assumption of additive normal error. That is, models where $\epsilon$ is
    modelled as an additive term on
    the logarithmic scale provide a better description of the data than models
    where $\epsilon$ is modelled as an additive term on the arithmetic scale.  
    We therefore used logarithmic-form models when assessing the
    effect of latitude on scaling relationships  with species richness.

@@

  \subsubsection*{Results}
    Contrary to the expected latitudinal gradient, the best-fit version of
    equation~(\ref{Latfull}) for species richness did not include a signficant effect of latitude for any ecosystem type except streams
    ($\beta_{Latitude}$=0.095, $p$=0.626; $\beta_{Latitude:Stream}$=-1.69, $p$=0.007).  This
    relationship was robust to the removal of three outliers (based on Cook's Distance). 
    There were also relationships between latitude and link density and between latitude and vulnerability
    in stream food webs, but these trends were non-signficant after the removal of three outliers.
    Link density and vulnerability did not vary with latitude in any other ecosystem type.
    The best-fit version of equation~(\ref{Latfull}) for generality did not include any effect of
    latitude in any ecosystem type.

@@

\begin{figure}[h]
\centerline{\includegraphics*[width=.75\textwidth]{Figures/by_TL/scaling_with_S/proportions/fitlines_nonts_observed.eps}}
\caption{Scaling relationships for link density, generality, 
and vulnerability relative to species richness and the proportions of basal resources (\% Basal),
intermediate consumers (\% Intermediate), top predators (\% Top), and species richness of a food web. 
For each relationship, we show observed values (white circles) and 
a simplified form of the scaling relationship described in equation XX (\emph{Main Text}), neglecting 
any effects of habitat type or latitude (black line, N=163 food webs). See Fig. 1 (\emph{Main Text}) to compare with 
observed values correcting for the effects of habitat type and latitude. }
\label{props_v_lat_obs}
\end{figure}

@@

\begin{figure}[h]
\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_proportions.eps}}
\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
types and over latitude. For each property we show the estimated scaling exponent for species richness (black
line) with its 95\% confidence interval (in grey),
based on N=163 empirical food webs. Latitude is 
given in degrees from the equator
regardless of direction.}
\label{S}
\end{figure}

\begin{figure}[!h]
\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/B_marginal_latitude_proportions.eps}}
\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
types and over latitude. For each property we show the scaling exponent for the proportion of
basal resources (black line) with its 95\% confidence interval (in grey), based on N=163 
empirical food webs. Latitude is given in degrees
from the equator regardless of direction.}
\label{B}
\end{figure}

@@

\begin{figure}[h]
\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/I_marginal_latitude_proportions.eps}}
\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
types and over latitude. For each property we show the scaling exponent for the proportion of
intermediate consumers (black line) with its 95\% confidence interval (in grey), based on 
N=163 empirical food webs. Latitude is given in degrees
from the equator regardless of direction.}
\label{I}
\end{figure}

\begin{figure}[!h]
\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/T_marginal_latitude_proportions.eps}}
\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
types and over latitude. For each property we show the scaling exponent for the proportion of
top predators (black line) with its 95\% confidence interval (in grey), based on N=163 
empirical food webs. Latitude is given in degrees
from the equator regardless of direction.}
\label{T}
\end{figure}
